Delta Factor - A New Authorization Factor

### 2022-08-08 paper1.tex
Rebels' code (implementation) included

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{article} 				%Short reports and scientific journals
% \documentclass{report}							% Books and thesis
\usepackage{graphicx}
\graphicspath{ {/Users/thomasperez/Desktop/finalpix/} }		%abs 
% \graphicspath{{../pdf/}{D:\ImagesforProjectLatex}}

@@

\noindent
Code type "pseudocode" (because of simplicity):\\
code\\
code\\

@@

%------------------------------------------------------------------------------%---------------------------------------
%------------------------------------------------------------------------------%---------------------------------------
\section{CITATIONS \normalfont{Chicago style:}} 	% Same as "References" as per prof
\noindent
Public Internet Standards (Various Authors)

>>>>

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{article} 				%Short reports and scientific journals
% \documentclass{report}							% Books and thesis
\usepackage[utf8]{inputenc}						% 128++ UTF-8 charset -----------------------
\usepackage{graphicx}
\graphicspath{ {/Users/thomasperez/Desktop/finalpix/} }		%abs 
% \graphicspath{{../pdf/}{D:\ImagesforProjectLatex}}

@@

%----------------------------------- <> % <>-----------------------------------
\noindent
\textbf{Code} type \textbf{"pseudocode"} (because of simplicity):\\
\noindent
Used existing HTTP Server code built into Py\\
\noindent
Developed a simple \textbf{COTP} algorithm from reference\\

\noindent
FOR INPUT:\\
\noindent
import hmac, base64, struct, hashlib, time\\

\noindent
def get\_hotp\_token(secret, msg):\\
\indent key = base64.b32decode(secret, true)\\

\# secret -\textgreater just unsigned bytes\\
\indent msg\_array = bytearray()\\
\indent msg\_array.extend(map(ord, msg))\\

\# RFC says to use specific bytes\\
\indent h = hmac.new(key, msg\_array, hashlib.sha1).digest()\\
\indent o = h[19] \& 15\\

\# Generate a hash using HMAC SHA1\\
\indent \# Grab the first 3 bytes after 20th, undo endiness\\
\indent key\_byte = struct.unpack(">l", h[o:o+4])[0]\\
\indent \# Convert key byte into a code\\
\indent htop =  (key\_byte \& 0x7fffffff) \% 1000000\\
\indent return htop\\

\noindent
EXAMPLE INPUT (from NGINX)\\
\noindent
tcp\_rtt=20380\\
\noindent
tls\_proto='TLSv1.3'\\
\noindent
tls\_csuite='TLS\_AES\_128\_GCM\_SHA256'\\
\noindent
secret='TESTTESTTEST===' \# 16 chars\\
%-----------
%-----------
%-----------

\noindent
FOR OUTPUT:\\
\noindent
def get\_cotp(secret):\\
\indent \# Gather 30sec timeframe from time - now!\\
\indent time\_Frame = (int(time.time())//30)\\
\indent \# Gather/extract out cipher suite + tcp RTT\\
\indent cipher\_suite = tls\_csuite 		         \# See above\\
\indent protocol\_version = tls\_proto		         \# See above\\
\indent tcp\_rt\t\_ms = (tcp\_rtt/1000)		         \# 34microsec\\      % known - sb '//' in py

\# Stitch everything together
msg = str(time\_Frame) + str(cipher\_suite) \indent + str(protocol\_version) + str(tcp\_rtt\_ms)\\

\# Ensuring to give the same OPT for 30sec\\
\indent cotp = str(get\_hotp\_token(secret, msg))\\

\# Adding 0 in the beginning till OTP has 6 digits\\
\indent while len(cotp) !=6:\\
 \indent \indent cotp += '0'\\

\indent \indent return cotp\\

\noindent
EXAMPLE OUTPUT\\
 \noindent
 COTP (30 second windows)\\
 \textbf{321009}\\
 \textbf{500028}\\ 
%----------------------------------- <> % <>-----------------------------------

@@

%------------------------------------------------------------------------------%---------------------------------------
%------------------------------------------------------------------------------%---------------------------------------
\section{CITATIONS \normalfont{(Chicago style):}} 	% Same as "References" as per prof
\noindent
Public Internet Standards (Various Authors)
